\textbf{Towards File System integrity verification in BTRFS}

### 2019-07-30 paper.tex
Clarify fs-verity's upstream and fs support status

\subsection{fs-verity}
Fs-verity\cite{FS-VERITY} works similar to dm-verity, but instead of a hash
tree for the whole block device, fs-verity has a Merkle-Tree for every file in
the File System hidden after the last block of the file, but hidden from the
normal File System operations and the user. The two differences to IMA are,
fs-verity a) uses a Merkle-Tree instead of a single hash, to speed up open(2)
calls and b) uses free space at the end of a file instead of an extended
attribute as this Merkle-Tree can grow larger than the maximum size of an
extended attribute. Fs-verity does not protect the File System's internal data
structures from being altered.

>>>>

\subsection{fs-verity}
Fs-verity\cite{FS-VERITY} works similar to dm-verity, but instead of a hash
tree for the whole block device, fs-verity has a Merkle-Tree for every file in
the File System hidden after the last block of the file, but hidden from the
normal File System operations and the user. The two differences to IMA are,
fs-verity a) uses a Merkle-Tree instead of a single hash, to speed up open(2)
calls and b) uses free space at the end of a file instead of an extended
attribute as this Merkle-Tree can grow larger than the maximum size of an
extended attribute. Fs-verity does not protect the File System's internal data
structures from being altered.\\
As of today (Linux Kernel v5.3-rc), fs-verity is only implemented for the ext4
and f2fs File Systems and not merged into the mainline kernel.
